Operator evolution from the similarity renormalization group and the Magnus expansion

### 2019-09-10 Notes/Operator_evolution/operator_evolution.tex
Started adding some figures to operator evolution notes
Added SRG-evolved potentials figures.

\noindent{%
-- Comparison of potential evolution with different regulators, orders, generators.
}
\\
-- Universality.
\\
-- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
\\
-- Use high cutoffs to transition to Magnus test problem.
\\
-- Example figure. EM N$^3$LO potential.
%
\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag2,00}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag3,00}%
	}
	\caption{Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
	\label{potential_contours_kvnn10_3S1}
\end{figure}

>>>>

\noindent{%
-- Comparison of potential evolution with different regulators, orders, generators.
}
\\
-- Universality.
\\
-- Discussion of high cutoffs, block-diagonal generator at high cutoffs, and how it handles spurious bound states.
\\
-- Use high cutoffs to transition to Magnus test problem.
%
\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_potential}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn106_3S1_Wegner_potential}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn222_3S1_Wegner_potential}%
	}
	\caption{NEED TO UPDATE THIS CAPTION: Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b and c).}
	\label{potential_contours_3S1_EM_RKE_Gezerlis_Wegner}
\end{figure}
%
\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Wegner_generator}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_potentials/potential_contours_kvnn10_3S1_Block-diag_generator}%
	}
	\caption{NEED TO UPDATE THIS CAPTION: Matrix elements of the Entem-Machleidt N$^3$LO non-local potential $V_{\lambda}(k, k')$ SRG-evolving in $\lambda$ right to left under transformations with the Wegner generator (a) and block-diagonal generators decoupling at $\Lambda=2$ and $3$ fm$^{-1}$ (b).}
	\label{potential_contours_3S1_EM_Wegner_Block-diag}
\end{figure}
